Remote Collection of Respiratory Samples

### 2024-11-22 Jordana Hoppe/Home Collection/manuscript.qmd
Home collection figures updated for Jordana

```{r libraries}
#| include: false
library(tidyverse)
library(lubridate)
library(gtsummary)
library(irr)
library(eulerr)
library(kableExtra)
library(caret)
library(likert)
library(patchwork)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Documents/GitHub",
  "Windows" = "C:/Users/Tim/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

  d %>%

@@

    plot(., quantities = T) %>%

@@

  p = ggplot(bar_plot_df, aes(x = name, fill = value, y = n)) +

@@

@@

@@

@@

```{r}
# List columns by number of possible answers
levels3 <- "q2.factor"
levels5 <- c("difficulty.factor", "shipping.factor")
checkboxes <- c(
  paste0("barriers___", 1:4, ".factor"),
  paste0("q6a___", 1:5, ".factor"),
  paste0("q6b___", 1:4, ".factor")
)
yn <- c(
  "q1.factor", "q3.factor", "previous.factor", "goodsample.factor", "q4.factor",
  "q5.factor", "q6.factor"
)
# Subset and label
t <- survey_data %>%
  filter(!participant_id %in% survey_exclude) %>%
  select(participant_id, q1.factor:q6b___4.factor)
labels <- as.character(label(survey_data)[sub("\\.factor", "", colnames(t))])
names(labels) <- colnames(t)
```

@@

```{r}
yn_df <- t %>%
  select(all_of(yn)) %>%
  rename(any_of(setNames(names(labels), labels)))
yn_df <- data.frame(lapply(yn_df, factor, levels = c("No", "Yes")), check.names = F)
p <- plot(likert(yn_df))
ggsave("Jordana Hoppe/Home Collection/Dissemination/Figures/yn.png",
  plot = p,
  width = 8, height = 6, units = "in"
)
```

@@

p_benefits <- plot(likert(benefits_df)) + ggtitle("Benefits") +
  theme(
    axis.text.x = element_blank(), axis.title.x = element_blank(),
    legend.position = "none"
  )
p_barriers <- plot(likert(barriers_df)) + ggtitle("Barriers")
p <- p_benefits / p_barriers
ggsave("Jordana Hoppe/Home Collection/Dissemination/Figures/check.png",
  plot = p,
  width = 8, height = 6, units = "in"
)
```

```{r}
df3 <- t %>%
  select(all_of(levels3)) %>%
  rename(any_of(setNames(names(labels), labels)))
p <- plot(likert(df3))
ggsave("Jordana Hoppe/Home Collection/Dissemination/Figures/q2.png",
  plot = p,
  width = 8, height = 6, units = "in"
)
```

```{r}
df5 <- t %>%
  select(all_of(levels5)) %>%
  rename(any_of(setNames(names(labels), labels)))
p <- plot(likert(df5))
ggsave("Jordana Hoppe/Home Collection/Dissemination/Figures/difficulty.png",
  plot = p,
  width = 9, height = 6, units = "in"
)
```

>>>>

```{r libraries}
#| include: false
library(tidyverse)
library(lubridate)
library(gtsummary)
library(irr)
library(eulerr)
library(kableExtra)
library(caret)
library(ggstats)
library(RColorBrewer)
library(patchwork)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Documents/GitHub",
  "Windows" = "C:/Users/Tim/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

  venn <- d %>%

@@

    plot(., quantities = T)

@@

  bar_plot <- ggplot(bar_plot_df, aes(x = name, fill = value, y = n)) +

@@

    scale_fill_manual(values = brewer.pal(3, "Accent")) +

@@

  p <- bar_plot + venn + plot_annotation(tag_levels = c("a", "b"))

@@

  # Save MSSA plot
  if (result_pattern == "results___1") {
    ggsave("Jordana Hoppe/Home Collection/Dissemination/Figures/mssa.png",
      plot = p,
      width = 12, height = , units = "in"
    bar_plot <- ggplot(
      bar_plot_df[bar_plot_df$name != "Delayed vs. Home", ],
      aes(x = name, fill = value, y = n)
      scale_fill_manual(values = brewer.pal(3, "Accent")) +
    p <- bar_plot + venn + plot_annotation(tag_levels = c("a", "b"))
    ggsave("Jordana Hoppe/Home Collection/Dissemination/Figures/mssa_2.png",
      plot = p,
      width = 12, height = , units = "in"

@@

```{r}
# List columns by number of possible answers
levels3 <- "q2.factor"
levels5 <- c("difficulty.factor", "shipping.factor")
checkboxes <- c(
  paste0("barriers___", 1:4, ".factor"),
  paste0("q6a___", 1:5, ".factor"),
  paste0("q6b___", 1:4, ".factor")
)
yn <- c(
  "q1.factor", "q3.factor", "q4.factor", "goodsample.factor",
  "q6.factor", "q5.factor", "previous.factor"
)
# Subset and label
t <- survey_data %>%
  filter(!participant_id %in% survey_exclude) %>%
  select(participant_id, q1.factor:q6b___4.factor)
labels <- as.character(label(survey_data)[sub("\\.factor", "", colnames(t))])
names(labels) <- colnames(t)
```

@@

```{r}
yn_df <- t %>%
  select(all_of(yn)) %>%
  rename(any_of(setNames(names(labels), labels)))
yn_df <- data.frame(lapply(yn_df, factor, levels = c("No", "Yes")),
  check.names = F
)
p <- gglikert(yn_df, sort = "none", cutoff = 1, add_totals = F) +
  scale_fill_manual(values = c("No" = "#D8B365", "Yes" = "#5AB4AC"))
p
ggsave("Jordana Hoppe/Home Collection/Dissemination/Figures/yn.png",
  plot = p,
  width = 8, height = 6, units = "in"
)
```

@@

p_benefits <- gglikert(benefits_df, add_totals = F) +
  ggtitle("Benefits") +
  theme(
    axis.text.x = element_blank(), axis.title.x = element_blank(),
    legend.position = "none"
  ) +
  scale_fill_manual(values = c("Unchecked" = "#D8B365", "Checked" = "#5AB4AC"))
p_barriers <- gglikert(barriers_df, reverse_likert = T, add_totals = F) +
  ggtitle("Barriers") +
  scale_fill_manual(values = c("Unchecked" = "#5AB4AC", "Checked" = "#D8B365"))
p <- p_benefits / p_barriers
p
ggsave("Jordana Hoppe/Home Collection/Dissemination/Figures/check.png",
  plot = p,
  width = 8, height = 6, units = "in"
)
```

```{r}
df3 <- t %>%
  select(all_of(levels3)) %>%
  rename(any_of(setNames(names(labels), labels)))
p3 <- gglikert(as_tibble(df3))
p3
ggsave("Jordana Hoppe/Home Collection/Dissemination/Figures/q2.png",
  plot = p3,
  width = 8, height = 6, units = "in"
)
```

```{r}
df5 <- t %>%
  select(all_of(levels5)) %>%
  rename(any_of(setNames(names(labels), labels)))
p5 <- gglikert(df5)
p5
ggsave("Jordana Hoppe/Home Collection/Dissemination/Figures/difficulty.png",
  plot = p5,
  width = 9, height = 6, units = "in"
)
p <- p3 / p5 + plot_annotation(tag_levels = c("a", "b"))
p
ggsave("Jordana Hoppe/Home Collection/Dissemination/Figures/fig2.png",
  plot = p,
  width = 9, height = 6, units = "in"
)
```
